---
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Importing and summarizing the data
```{r}
bank <- read.csv("~/NEU_COURSES/Stastical_methods_in_Eng/Project/bank-full.csv", sep=";")
```
```{r}
summary(bank)
```
Checking for duplicates and missing variables
```{r}
library(data.table)
bank <- as.data.table(bank)
bank[duplicated(bank)]
sum(!complete.cases(bank))
sapply(bank, function(x) sum(is.na(x)))
```
The data doesn't have any duplicates or missing values.

```{r}
str(bank)
```



The Target variable is skewed towards 0(NO)

Boxplots analyzing Outliers
```{r}
library(ggplot2)
library(pdp)
p1 <- ggplot(bank, aes(x='', y=age)) + 
  geom_boxplot()
p2 <- ggplot(bank, aes(x='', y=balance)) + 
  geom_boxplot()
p3 <- ggplot(bank, aes(x='', y=day)) +
  geom_boxplot()
p4 <- ggplot(bank, aes(x='', y=duration)) +
  geom_boxplot()
p5 <- ggplot(bank, aes(x='', y=campaign)) +
  geom_boxplot()
grid.arrange(p1,p2,p3,p4,p5,ncol =3,nrow=2)
```
Some Visualizations are performed for better understanding of the data:

```{r}
barp1 <-ggplot(data=bank, aes(x=y, y='')) +
  geom_bar(stat="identity", fill="steelblue")+ggtitle("Total Term Deposit Subcriptions") +
         xlab(" Term Deposit Subscriptions")
barp1
```

The Target variable is clearly skewed towards 0(NO)

Barplots:
```{r}
barp2 <- ggplot(data = bank, aes(x=job, fill=y)) +
         geom_bar() +
         ggtitle("Term Deposit Subscription based on Job") +
         xlab(" Job") + guides(fill=guide_legend(title="Subscription of Term Deposit")) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
barp2
barp3 <- ggplot(data = bank, aes(x=education, fill=y)) + geom_bar() +
         ggtitle("Term Deposit Subscription based on Education") +
         xlab("Education") + guides(fill=guide_legend(title="Subscription of Term Deposit")) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
barp3
barp4 <- ggplot(data = bank, aes(x=marital, fill=y)) + geom_bar() +
         ggtitle("Term Deposit Subscription based on Marital") +
         xlab("Marital") + guides(fill=guide_legend(title="Subscription of Term Deposit")) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
barp4
```

Scatterplots:

```{r}
Scatterp1 <- ggplot(data = bank, aes(x=campaign,y=duration, color=y)) + geom_point() +
         ggtitle("Duration vs Campaign for Subscription of Term Deposit") +
         xlab("Campaign") + guides(color=guide_legend(title="Subscription of Term Deposit")) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
Scatterp1
```
Changing Target variable to binary
```{r}
bank$y = ifelse(bank$y=='yes',1,0)
str(bank)
summary(bank)
prop.table(table(bank$y))
```
Correlation matrix:
```{r}
bank.select <- bank[,c(6,7,8,10,11,12,13,17)]
pairs(bank.select)
```
```{r}
library(GGally)
bank1 <- bank[,c(1,6,10,12,13,14,17)]
ggpairs(bank1)
```
```{r}
bank2 <- bank[,c(1,2,3,4,5,6,7,17)]
pairs(bank2)
```

```{r}
bank3 <- bank[,c(8,9,10,11,12,13,14,15,16,17)]
pairs(bank3)
```

Splitting Training and testing data:

```{r}
library(caTools)
set.seed(123)
split = sample.split(bank$y,SplitRatio = 0.75)
training_set = subset(bank, split == TRUE)
test_set = subset(bank, split == FALSE)
```

Scaling Numeric Variables
```{r}
training_set[,c(1)] <- scale(training_set[,c(1)])
training_set[,c(6)] <- scale(training_set[,c(6)])
training_set[,c(10)] <- scale(training_set[,c(10)])
training_set[,c(12)] <- scale(training_set[,c(12)])
training_set[,c(13)] <- scale(training_set[,c(13)])
test_set[,c(1)] <- scale(test_set[,c(1)])
test_set[,c(6)] <- scale(test_set[,c(6)])
test_set[,c(10)] <- scale(test_set[,c(10)])
test_set[,c(12)] <- scale(test_set[,c(12)])
test_set[,c(13)] <- scale(test_set[,c(13)])
```

Building a Logistic Regression model:
```{r}
classifier.lm = glm(formula = y ~ .,
                 family = binomial,
                 data = training_set)
```
```{r}
pred_lm = predict(classifier.lm, type='response', newdata=test_set[,-17])
```
```{r}
predicted_y <- data.frame(y = test_set$y, pred = NA)
predicted_y$pred <- pred_lm
```
Confusion matrix:
Finding the Optimum Cutoff
```{r}
library(InformationValue)
optCutOff <- optimalCutoff(test_set$y, pred_lm)[1] 
optCutOff
```
```{r}
Results <- confusionMatrix(test_set$y, pred_lm, threshold = optCutOff)
Results
```

Summary of the Regression Model

```{r}
summary(classifier.lm)
```
```{r}
misClassError(test_set$y, pred_lm, threshold = optCutOff)
```
```{r}
plotROC(test_set$y, pred_lm)
```
```{r}
Concordance(test_set$y, pred_lm)
```
```{r}
sensitivity(test_set$y, pred_lm, threshold = optCutOff)
specificity(test_set$y, pred_lm, threshold = optCutOff)
```
```{r}
accuracy = (Results['1','1']+Results['0','0'])/(Results['0','1'] + Results['1','0'] + Results['1','1'] + Results['0','0'])
accuracy
```
